

\begin{abstract}
    本文档阐述 \suepthesis{} v\version{} 的使用方法，包括其编译方式、文档类选项以及提供的功能。
    希望能够帮助读者快速便捷地完成学位论文排版。
  
    \suepthesis{} 旨在以最简实现和最小依赖完整覆盖上海科技大学本科及研究生学位论文的所有格式要求，
    且不为用户额外设限。使用时仅需指定 documentclass 为 \suepthesis{} 即可满足基本排版要求。
    文档通过 \verb|\suepsetup| 命令统一设定学位论文信息，且仅提供满足格式需求的最少额外命令以保证兼容性。
    用户可根据自身撰文习惯，引入额外的宏包和命令完成学位论文撰写。

    \suepsetup{
      % 中文摘要关键字
      keywords = {上海电力大学；学位论文；\LaTeX{}},
    }
\end{abstract}


\begin{abstract*}
  Based on researching for several years, Delphi7 and ODBC are utilized to develop Transformer Fault Diagnosing Expert System (TFDES) based on Access database. Fault Diagnosis is based on expert knowledge base, composed by experts’ experiences. Latent Fault Diagnostic (LFD) and Insulation Precautionary Test (IPT) are popularly used in reality ,so as to diagnose faults of transformers’ insulation. LFD, is used to indicate the latent faults of transformers, based on Dissolved Gas Analysis (DGA), and assisted by External Examination (EE), Insulation Oil (IO).IPT, consisted of Insulation Resistance ,Ohmic Resistance, Oil Dielectric Loss ,DC leaking Current and Bushing. Through LFD and ITP, TFDES can judge synthetically the whole insulation level of transformer, and give out proper expert suggestions to operators. This TFDES , completed through a lot of investigation and researching, affiliated with Test Report and some other functions, thinking completely of on-the-spot need, is very worthy practically.
  
  \suepsetup{
    % 英文摘要关键字
    keywords* = {Shanghai University of Electric Power, Thesis, \LaTeX{}}
  }
\end{abstract*}